### 2017-09-27 Writing/draft.tex
Conclusion updated

We found that Character Differences as a proxy for character correlation have a strong effect on the recovering the ``normal'' topology

 is not a problem \textit{per se} as long as characters are not actively coded to be similar.
On the other hand, actively selecting characters based to favour independence does not highly increase the ability of recovering tree topology (compared to simply bootstrapping a matrix - at least for modest size matrices).
We hope that these results will encourage researchers working on discrete morphological characters to continue exploring morphology through discrete characters to better understand the Tree of Life.

>>>>

We found that Character Differences as a proxy for character correlation have a strong effect on the recovering the ``normal'' topology: when character correlation was high (low Character Differences), the topology was always the furthest away from the ``normal'' topology.
Conversely, when correlation between characters was low, the topology was always the closest to the ``normal'' topology.
These results seems independent on the size of the matrix (number of taxa and/or characters) but can be influenced by the phylogenetic inference method used with Bayesian inference faring better in terms of clade conservation, especially in larger matrices.

However, in modest size matrices (25 taxa 100 to 350 characters), the effect of actively choosing to minimise character correlation was not more significant than simply bootstrapping the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
We hope that these results will encourage researchers working on discrete morphological characters to continue exploring morphology through discrete characters to better understand the Tree of Life.
